---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/anhoej/cprr.svg?branch=master)](https://travis-ci.org/anhoej/cprr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/cprr)](https://cran.r-project.org/package=cprr)

# cprr

Calculate date of birth, age, and gender, and generate anonymous sequence numbers from CPR numbers. Also modulo 11 check is available, though this function is only relevant for cpr numbers until 2007.

## Examples

```{r example}
# Load cprr.
library(cprr)

# Make vector of example cpr numbers.
cpr <- c('1508631111', '020962-4444', '131076-2222', '1508631111', '2110625629')

# Caluculate dates of birth from cpr numbers.
dob(cpr)

# Calculate ages from cpr numbers.
age(cpr)

# Calculate genders from cpr numbers.
gender(cpr)

# Generate anonymous sequence numbers from cpr numbers.
scramble(cpr)

# Perform modulo 11 check of cpr numbers.
mod11(cpr)

# Make data frame from build in data set of official test cpr numbers.
cpr <- test_cpr$cpr
data.frame(
  cpr    = cpr,
  id     = scramble(cpr),
  dob    = dob(cpr),
  gender = gender(cpr),
  mod11  = mod11(cpr)
)
```


## Installation

You can install development version from github:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("anhoej/cprr")
```

Or stable version from CRAN:

```{r cran-installation, eval = FALSE}
install.packages("cprr")
```

## About CPR numbers

The Danish Personal Identification number (Danish: *CPR-nummer* or *personnummer*) is a national identification number, which is part of the personal information stored in the Civil Registration System (Danish: *[Det Centrale Personregister](https://www.cpr.dk/)*).

It is a ten-digit number with the format DDMMYY-SSSS, where DDMMYY is the date of birth and SSSS is a sequence number. The first digit of the sequence number encodes the century of birth (so that centenarians are distinguished from infants), and the last digit of the sequence number is odd for males and even for females.

The civil register lists only persons who:

* Are born in Denmark of a mother already registered in the civil register, or 
* have their birth or baptism registered in a ’Dansk Elektronisk Kirkebog (DNK)’ (Danish electronic church-book), or 
* reside legally in Denmark for 3 months or more (non-Nordic citizens must also have a residence permit).

Danish citizens, including newborn babies, who are entitled to Danish citizenship, but are living abroad, do not receive a personal ID number, unless they move to Denmark.

Source: https://en.wikipedia.org/wiki/Personal_identification_number_(Denmark)
